\documentclass[11pt]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

% \addbibresource{bibliography.bib} % Specify the bibliography file to include publications

%\usepackage{wasysym}
%\usepackage{marvosym}
\usepackage{fontspec}
\usepackage{fontawesome}

%\newfontfamily{\FA}{FontAwesome Regular}

\newfontfamily{\FA}{FontAwesome}

\begin{document}

\header{Nolan}{Essigmann}{developer + mathematician who loves solving problems}
% {\color{red} $\varheartsuit$}
%{Goal: Challenging position in a field that uses or could use mathematical tools to solve complex problems} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
229 Vassar Street
Cambridge
Massachusetts 02139
%~
%\phone \ +1 (617) 225 1403
%\phone \ 75114 77006
% UK number
+1 (857) 259 0407
%~
{{\FA \faEnvelope} Email}
{\footnotesize nhessigmann@gmail.com}
{{\FA \faGithub} Github}
{\footnotesize \href{http://github.com/nessig}{github.com/nessig}}
{{\FA \faHome} Website}
{\footnotesize \href{https://nessig.github.io}{ nessig.github.io}}
% \Email \ nessig@mit.edu
\section{programming languages}
{\color{red} $\varheartsuit$} Python
JavaScript, Go
C++, Julia, SQL
CSS3 \& HTML5
% \section{compotencies? use thesaurus}
\section{interests\\ \& activities}
software engineering
web development
data science
statistics
% learning
teaching
forestry
% hiking
g\={o}j\={u}-ry\={u} karate
cycling
EMT
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}

%------------------------------------------------

\entry
{2010--2015}
{Bachelor of Science in Mathematics}
{\textbf{Massachusetts Institute of Technology}}
% {I focused on experimental mathematics, which uses numerical computation to investigate mathematical objects.}
% {In my undergraduate I focused on experimental mathematics, which uses numerical computation to investigate mathematical objects, and pure mathematics, which involves the creation and study of abstractions.}
{% Focused on experimental mathematics, which uses numerical computation to investigate mathematical objects, and pure mathematics, which involves the creation and study of abstractions.
Focus on experimental math using computation to investigate mathematical objects, and pure math: the creation and study of abstractions.
}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}
\begin{entrylist}
\entry
%{June 2014 - August 2014}
{summer 2015}
% {Micmac Environmental Lab,\\The Aroostook Band of Micmacs}
{Micmac Environmental Health Lab}{The Aroostook Band of Micmacs}
% {\footnotesize Presque Isle, Maine}
%{\footnotesize Presque Isle, Maine}
{\emph{Volunteer Lab Technician in Environmental Health} \\
%Make clear on reservation. Ask rosie if ppl will understand reservation. Frame more as ashort term experience vs. job.
% Repaired Atomic Absorption Spectrometer, saving the lab enough money to hire a new technician (Change language to seem more heroic?).}\\
Repaired atomic absorption spectrometer for the Micmac Tribe, allowing them to test tribal waters for toxins in-house; work helped create a new revenue engine.}

\entry
{2013-2014}
{Laboratory of Professor Adam Arkin}{University of California, Berkeley\\ {\null} \hfill {Lawrence Berkeley National Laboratory}}%{Lawrence Berkeley National Laboratory}
%{\footnotesize Berkeley, California}
%{\addfontfeature{Color=lightgray}  Lawrence Berkeley National Laboratory}\\
{\emph{Undergraduate Researcher in Synthetic and Systems Biology}\\
Spent gap year working at UC Berkeley designing high-throughput protein-protein interactomics pipelines using Python and SQL.}
%\begin{itemize}
%\item Worked on high throughput protein-protein interactomics assays.
%% \item Undergraduate researcher in synthetic and systems biology laboratory, working on high throughput protein-protein interactomics assays
%\item Worked on a metagenomics and environmental genomics project, optimizing pipeline for high throughput functional annotation of genomes from large set of diverse microbes
%%\item Techniques used: cutting edge cloning and transposon mutagenesis techniques; next generation high throughput genome sequencing; automated/robotic cell culturing, colony counting, and growth measurement; Zeiss AxioLab.A1 microscopy to assess microbial morphology; many more
%\item[Techniques used:] Statistical bioinformatic methods, genome sequence alignment algorithms, utilizing simple MySQL scripts to aggregate important growth condition data from various databases, writing simple Python web scraping scripts using BeautifulSoup and regex
%\end{itemize}
%}\\

\entry
%{June 2011 - August 2012}
{2011-2012}
{Laboratory of Professor Alice Ting}{Massachusetts Institute of Technology}
% {\footnotesize Cambridge, Massachusetts}
{\emph{Undergraduate Researcher in Chemical Biology} \\
Used genetic engineering tools along with molecular modeling Python libraries to design and rationally construct molecular sensors. Interim lab manager.}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS
%----------------------------------------------------------------------------------------

\section{technical skills}
\begin{description}
\item[Backend] Python: significant exp. developing applications/services. Julia and C++: exp. writing and utilizing out-of-core, vectorized, and cache-friendly algorithms/DS. Golang: exp. with distributed messaging systems and implementation of common concurrency patterns. Exp. with Flask, Django, cherrypy, 
unittest/mock,
ZeroMQ,
Redis,
Postgres,
Neo4j,
MongoDB,
Gunicorn,
*nix,
Google (GAE, GCE),
Docker (kubernetes, Zipkin),
Valgrind,
Nginx.
\item[Frontend]
React (npm, webpack, babel, ES6-7),
Redux,
D3.js,
Angular (1.x),
SASS,
Bootstrap,
Material-UI,
Materialize.
\item[Statistics] Exp. in theory and application of statistics and machine learning. {\color{red} $\varheartsuit$} Pandas.
\end{description}

\section{projects}
\begin{description}
\item[2D Root Visualizer] Web app/service for visualizing fractals written in C++, Python, and Javascript. Tools used: OpenMP, ZeroMQ, Websockets, and HTML5 Canvas.
\item[Riemann Hypothesis Verification] Tools to computationally verify the Riemann Hypothesis for trillions of zeros and the statistical analysis of the zeros of the Riemann Zeta function and the spectra of random Hermitian matrices (Python, Julia, C++).
\item[Business Intelligence Dashboard] React app for realtime(ish) reporting of BI data. React, D3.js (for math, not DOM manipulation), Go, Neo4j, MongoDB.
% \item[Flask Social Network] Bare bones Flask social network/blog with full text search using minimal extensions. Tools: PostgreSQL, Long polling, D3.js.
\end{description}

\end{document}




